Separating Use and Reuse to Improve Both

### 2017-05-25 FACS/Conclusion.tex
.

\section{Conclusions and practical applications}

@@

We show how our model can be easly extended with more operators, if they behave well with respect to a simple predicate.

In order to focus on the explanation of the high level concepts, this paper do not present formalism for our approach.
Formalism for similar approaches can be found in[deefjig, myThesis].

We are working on 42: a full blown language 
that leverage on the ideas presented in this paper to obtain reliable and understandble metaprogramming.
Formalization (in progress) for such language can be found at URLURLURL.
42 extands our model allowing
flattening to execute arbitrary computations.
In such model we do not need an explicit notion of traits: they are encoded as method returning a code literal.

  In addition to this, 42 have feature less related to code composition, like
  a strong type system supporting aliasing mutability[] and circularity control[],
   checked exceptions[], errors (unchecked exceptions) with strong exception safety for errors[].

42 do not have a finite set of composion operators; they can be added using the built in support for native method calls. They can be dynamically checked to verify that they are well behaved according to our predicate, or they can be trusted to acheive efficiency.

%\item more operators can be accomodated without changing the general model

>>>>

\section{Conclusions, extensions and practical applications}

@@

The model presented here is very easy to extend:
For example nested classes can be easly added,giving us enough power to easly solve the expression problem as in \cite{deep}. More composition operators can be added in addition to \use.
In particular all the sophisticated operators of \cite{deep} could be added.
 Indeed we can add any operator respecting following criteria:

\begin{itemize}
\item As for \use, the operator does not need to be total, but if it fails it needs to provide an error that will be reported to the programmer.
\item When the operator takes in input only traits (they are going to be well typed), if a result is produced,
 such result is well typed.
\item When the operator takes in input also code literals, if a non well typed result is produced,
the type error must be tracked back to code in one of those non typed yet code literals.
 \end{itemize}

 Our simplified model represent the conceptual core of  a novel full blown programming language 
 (\verb@http://L42.is@),
that leverage on the ideas presented in this paper to obtain reliable and understandble metaprogramming.
Formalization (in progress) for such language can be found at 
\verb@github.com/ElvisResearchGroup/L42/tree/master/Main/formal@.
L42 extands our model allowing
flattening to execute arbitrary computations.
In such model we do not need an explicit notion of traits: they are encoded as method returning a code literal.
L42 also have feature less related to code composition, like
  a strong type system supporting aliasing mutability and circularity control,
   checked exceptions, errors (unchecked exceptions) with strong-exception-safety for errors.

L42 do not have a finite set of composion operators; they can be added using the built in support for native method calls. They can be dynamically checked to verify that they are well behaved according to our predicate, or they can be trusted to acheive efficiency.
